Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-27 analysis/paper/hotspots-paper.Rmd
simplified R code dealing with multipanel figs

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "7/27/2019"
bibliography: research.bib
output: 
  bookdown::html_document2
---

@@

```{r define_nfig}
nfig <- c(2, 2, 3, 3, 1) # number of panel figs per hotspot
names(nfig) <- paste0("Chr", c(2, 5, 7, 11, 13))
```

```{r panel1, fig.cap = paste0("Chr", hot_chr, "hotspot scatter plots of mediation LOD difference against pleiotropy LOD, separated by local trait.")}
include_graphics(paste0("../figures/Chr", hot_chr, "_scatter-panel1.pdf"))
```

```{r panel2, eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 1}
include_graphics(paste0("../figures/Chr", hot_chr, "_scatter-panel2.pdf"))
```

```{r panel3, eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 2}
include_graphics(paste0("../figures/Chr", hot_chr, "_scatter-panel3.pdf"))
```

```{r def-5}
hot_chr <- 5
```

```{r fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 5 hotspot."}
#include_graphics("../figures/Chr5_scatter.pdf")
```

```{r ref.label = "panel1", fig.cap = paste0("Chr", hot_chr, "hotspot scatter plots of mediation LOD difference against pleiotropy LOD, separated by local trait.")}
```

```{r ref.label = "panel2", eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 1}
```

```{r ref.label = "panel3", eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 2}
```

```{r def-7}
hot_chr <- 7
```

```{r fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 7 hotspot."}
#include_graphics("../figures/Chr7_scatter.pdf")
```

```{r ref.label = "panel1", fig.cap = paste0("Chr", hot_chr, "hotspot scatter plots of mediation LOD difference against pleiotropy LOD, separated by local trait.")}
```

```{r ref.label = "panel2", eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 1}
```

```{r ref.label = "panel3", eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 2}
```

```{r def-11}
hot_chr <- 11
```

```{r fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 11 hotspot."}
#include_graphics("../figures/Chr11_scatter.pdf")
```

```{r ref.label = "panel1", fig.cap = paste0("Chr", hot_chr, "hotspot scatter plots of mediation LOD difference against pleiotropy LOD, separated by local trait.")}
```

```{r ref.label = "panel2", eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 1}
```

```{r ref.label = "panel3", eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 2}
```

```{r def-13}
hot_chr <- 13
```

```{r fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 13 hotspot."}
#include_graphics("../figures/Chr13_scatter.pdf")
```

```{r ref.label = "panel1", fig.cap = paste0("Chr", hot_chr, "hotspot scatter plots of mediation LOD difference against pleiotropy LOD, separated by local trait.")}
```

```{r ref.label = "panel2", eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 1}
```

```{r ref.label = "panel3", eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 2}
```

\section{Discussion}

@@

\printbibliography

```{r install_here}
install.packages("here", repos = "https://cloud.r-project.org")
```

\subsection{Colophon}

This report was generated on \Sexpr{Sys.time()} using the following computational environment and dependencies:

\begin{singlespacing}
%\begin{landscape}
```{r colophon, cache = FALSE, echo = TRUE, tidy.opts=list(width.cutoff=50), size = "tiny", results = "markup"}
# which R packages and versions?
foo <- devtools::session_info()
readr::write_csv(x = foo$packages, path = "packages.csv")
knitr::kable(tibble(field = names(foo$platform), value = unlist(foo$platform)))
foo$packages %>%
  as_tibble() %>%
  dplyr::select(-4, -5, -10, -11) %>%
  knitr::kable()
```

%\end{landscape}

\end{singlespacing}

>>>>

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "7/27/2019"
bibliography: research.bib
output: 
  - bookdown::html_document2
  - github_document:
      toc: true
      toc_depth: 2
---

@@

# Discussion

@@

# Colophon

This report was generated on ` r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE, echo = TRUE, tidy.opts=list(width.cutoff=50), size = "tiny", results = "markup"}
# which R packages and versions?
devtools::session_info()
```
